draft

### 2025-05-26 draft.tex

\begin{figure}[htbp]
\centering
\includegraphics[width=.99\linewidth]{./figs/fig_1_tmp.png}
\caption{\label{fig:overview}cp\_measure generates features from images by using information in every region of interest ("object"). It can featurize the pairwise combination of all the available channels (colours) and objects. The resultant matrices represent the entire experiment and can be studied using statistical, machine, and deep learning methods.}
\end{figure}

@@

\bibliographystyle{icml2025}
\bibliography{bibliography}
\section{Appendix}
\label{sec:orgdd18dd8}
\subsection{Methods}
\label{sec:orgb3e9382}
\subsubsection{Data and software}
\label{sec:orgbda0ae2}
The codebase for cp\_measure is available on \url{https://anonymous.4open.science/r/cp\_measure-B0DA}. All code to reproduce the analyses and figures, alongside links to the original data, is available on the GitHub repository \url{https://github.com/afermg/2025\_cpmeasure/}. The datasets we produced for this work are available on Zenodo. The selection of samples from JUMP and the images can be found on \url{https://zenodo.org/records/15390631/latest}. The image-based profiles produced with Cellprofiler and used for the comparisons in Figure 2 can be on \url{https://zenodo.org/records/15505477/latest}.

\subsubsection{Acknowledgements}
\label{sec:acknowledgements}

>>>>

\begin{figure}[htbp]
\centering
\includesvg[width=.99\linewidth]{./figs/cpmeasure_overview.svg}
\caption{\label{fig:overview}cp\_measure generates features from images by using information in every region of interest ("object"). It can featurize the pairwise combination of all the available channels (colours) and objects. The resultant matrices represent the entire experiment and can be studied using statistical, machine, and deep learning methods.}
\end{figure}

@@

\bibliographystyle{icml2025}
\bibliography{bibliography}
\section{Appendix}
\label{sec:orgdd18dd8}
\subsection{Methods}
\label{sec:orgb3e9382}
\subsubsection{Data and software}
\label{sec:orgbda0ae2}
The codebase for cp\_measure is available on \url{https://anonymous.4open.science/r/cp\_measure-B0DA}. All code to reproduce the analyses and figures, alongside links to the original data, is available on the GitHub repository \url{https://anonymous.4open.science/r/2025_cpmeasure-3FBF}. 
%The datasets we produced for this work are available on Zenodo. The selection of samples from JUMP and the images can be found on \url{https://zenodo.org/records/15390631/latest}. The image-based profiles produced with Cellprofiler and used for the comparisons in Figure 2 can be on \url{https://zenodo.org/records/15505477/latest}.
% 
\subsubsection{Acknowledgements}
\label{sec:acknowledgements}
